Pulling oral and IV data from CvTdb

### 2023-11-07 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Slightly more stringent filtering for the creation of the cvt data set and adjusting the calc_loq_factor for imputed LOQs

# Some pentachloranisole studies
# S0361 seems to have some data that has not been extracted (also for mouse)
cvt_df <- cvt_df %>%
  mutate(loq = case_when(
    other_study_identifier %in% "S0361" ~ 0.05,
    other_study_identifier %in% "S0328" ~ 1, # This is inferred
    # Highest value under loq is 0.9
    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
    .default = loq
  ),
  loq_units = case_when(
    other_study_identifier %in% "S0361" ~ "ug/mL",
    other_study_identifier %in% "S0328" ~ "ug/mL",
    .default = loq_units
  ))

@@

>>>>

# Some pentachloranisole studies
# S0361 seems to have some data that has not been extracted (also for mouse)
cvt_df <- cvt_df %>%
  mutate(loq = case_when(
    # here omitted a change to a value for LOQ that doubles the minimum detected limit
    other_study_identifier %in% "S0328" ~ 1, # This is inferred from the data
    # Highest value under loq is 0.9
    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
    # The method of imputation for loq may yet need to be improved
    .default = loq
  ),
  loq_units = case_when(
    other_study_identifier %in% "S0361" ~ "ug/mL",
    other_study_identifier %in% "S0328" ~ "ug/mL",
    .default = loq_units
  ))

@@

# This is the final filtering so that the dataset is most consistent with the
# most current near future pull in the new year
cvt_df <- cvt_df %>%
  filter(!is.na(analyte_dtxsid),
         analyte_dtxsid == test_substance_dtxsid,
         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
         !(other_study_identifier %in% c("S0916")),
         !(analyte_name_original %in% "Methemoglobin"),
         is.na(radiolabeled))

cvt_df %>%
  filter(conc > 0) %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  distinct() %>%
  count() %>% 
  ungroup() %>%
  filter(n >= 10) %>% 
  distinct(analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  arrange(analyte_dtxsid, species, document_id) %>%
  left_join(cvt_df) %>% 
  View()

cvt_df %>%
  filter(conc > 0) %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, document_id,
           dose_level_normalized) %>%
  distinct() %>%
  count() %>%
  ungroup() %>%
  count(n)
```

This filtered and transformed dataset has 14,486 observations.
